% Kompiuterijos katedros šablonas
% Template of Department of Computer Science II
% Versija 1.0 2015 m. kovas [ March, 2015]

\documentclass[a4paper,12pt,fleqn]{article}
\input{allPacks}

\newtoggle{inLithuanian}
 %If the report is in Lithuanian, it is set to true; otherwise, change to false
\settoggle{inLithuanian}{false}

%create file preface.tex for the preface text
%if preface is needed set to true
\newtoggle{needPreface}
\settoggle{needPreface}{false}

\newtoggle{signaturesOnTitlePage}
\settoggle{signaturesOnTitlePage}{true}

\input{macros}

\begin{document}
% #1 -report type, #2 - title, #3-7 students, #8 - supervisor
\depttitlepage{Bachelors Thesis}{Implementation of application for visualization of regularities and randomness in data}{Audrius Baranauskas}
{}{}{}{}% students 2-5
{dr. Tadas Meškauskas}

\tableofcontents


%keywords and notations if needed
\sectionWithoutNumber{Keywords}{keywords}{Pateikiamas terminų sąrašas (jei reikia)}

%both abstracts
\bothabstracts{\input{abstract}}%tex-file of abstract in original language
{Darbo pavadinimas kita kalba} %if work is in LT this title should be in English
{\input{abstractEN}}%tex-file of abstract in other language


%Introduction section: label is sec:intro
\sectionWithoutNumber{\keyWordIntroduction}{intro}
\input{introduction.tex}


%=============================================================
%========================The main part========================
%=============================================================

\newpage

\section{Signal processing and Recurrence plot}
\label{sec:motivation}
\subsection{Signal processing}

A signal is a function that conveys information about the behaviour of a system
or attributes of some phenomenon \cite{priemer1990introductory}.
For example, measuring the time taken between a weight-driven
pendulum clock's ticks produces signal.
In turn, for the scope of this paper, we defined the term signal processing as
\textit{the science of analyzing time-varying processes} 
\cite{lyons2004understanding}.
By processing a signal we analyzed the non-triviality of a given signal.
Analyzing a signal reveals that some signals 
have properties that can be categorized.

\subsection{Signal property categories}


We have considered the following categories:
\begin{enumerate}
  \item Stationary and non stationary signals
  \item 
\end{enumerate}


Signals have varying properties. Some consist of simple repetitions while others
have no apparent patterns.
For example, measuring the time taken between a weight-driven
pendulum clock's ticks produces a relatively simple (trivial) signal.


% For the scope of this paper, we defined the term signal 
% processing as \textit{the science of analyzing time-varying 
% processes} \cite{lyons2004understanding}.




% \subsection{Signal classification}
% Signals have several classes. For the scope of this paper we considered
% the classes \cite{lathi1998signal}:
% \begin{enumerate}
%   \item Stationary and non-stationary signals
%   \item 
%   \item Periodic, quasi periodic and aperiodic signals 


% \end{enumerate}






% Some signals are inherently simple such as the time taken
% a falling object or

% \begin{lstlisting}
%   sygnalStates = []

%   # Generate data pairs, tripplets, quadruplets... D - plets
%   for i in range(0, self.M):
%       state = []

%       for j in range(0, self.D):
%           state.append(self.data[i+(j*self.d)])

%       sygnalStates.append(state)
% \end{lstlisting}


\newpage
\section{Web application development}


\newpage
\section{Pirmasis skyrius}
\label{sec:motivation}




\subsection{Pirmojo skyriaus poskyris}
\label{sec:example}
Pateikiamas \ref{sec:example} poskyrio tekstas. Vienas iš šaltinių~\cite{KTZ}. Visas ~\cite{KTV} turinys priklauso \ref{sec:motivation} skyriui.

\subsubsection{Pirmojo skyriaus pirmo poskyrio poskyris}
\label{sec:data}
Pateikiamas trečio lygio poskyrio tekstas.

\begin{equation}
  x = \sum_{i=1}^N m_i
\end{equation}

\begin{table}[!ht]\centering
  \caption{Lentelė ... }
  \label{tabl:table}
  \begin{tabular}{l|r|}
    test & test \\ \hline
    test & test \\
  \end{tabular}
\end{table}

Sprendimas pristatomas \ref{alg:1} algoritme, o įgyvendinimas -- \ref{abc} išeities kode.

\begin{algorithm}\caption{Algoritmas uždavinio sprendimui}
  \label{alg:1}
  \begin{algorithmic}
    \REQUIRE
    \ENSURE
    \STATE a \AND b
  \end{algorithmic}


\end{algorithm}



\begin{lstlisting}[caption={Pagrindinio metodo žingsniai},label={abc}]
public static void main(String args[]){
}
\end{lstlisting}

%Conclusions section
\sectionWithoutNumber{\keyWordConclusions}{conclu}
\input{conclusions.tex}

%ateities darbų gairės, planas/next steps of the work
\sectionWithoutNumber{Ateities tyrimų planas}{future}{Pristatomi ateities darbai ir/ar jų planas, gairės tolimesniems darbams....}


%file literatureSources.bib
\referenceSources{literatureSources}



%% this part is optional
\newpage
\begin{appendices}
  Dokumentą sudaro du priedai: \ref{app:a} priede  ....
  \newpage
  \section{Pirmojo priedo pavadinimas}
  \label{app:a}
  Pirmojo priedo tekstas ...

  \newpage
  \section{Antrojo priedo pavadinimas}
  Antrojo priedo tekstas ...

\end{appendices}


\end{document}
